Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-16 BN_discretizer_paper.tex
add $$
Add experiment part

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{bm}
\usepackage{graphicx} % Allows including images
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{amsfonts} % for mathbb
\usepackage{tikz}
% \usepackage[capitalize]{cleveref}
\usetikzlibrary{bayesnet}
\setcitestyle{aysep={ }} %Author-Year Separator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

@@

Forward sampling is used to draw samples from the joint distribution represented by a Bayesian network.
Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
Furthermore, the parent\rightarrow child sampling order can be reversed if the marginal probability of the child variable is known.
By Bayes' rule,

@@

A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from $\mathbb{R}$ to $\brock{1,2,3,\ldots,k}$ such that
\begin{equation}
  M_C (x)=\begin{cases}
    1, & \text{if $x<t_1$}.\\
    i, & \text{if $t_{i-1} \leq x < t_i$}\text{.}\\
    k, & \text{if $t_{k-1} \leq x$}
  \end{cases}
\end{equation}

@@

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{lscape}
\usepackage{caption}
% \usepackage[capitalize]{cleveref}
\usetikzlibrary{bayesnet}
\setcitestyle{aysep={ }} %Author-Year Separator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

@@

Forward sampling is used to draw samples from the joint distribution represented by a Bayesian network.
Variables are sampled in topological order such that parental instantiations are always known~\citep[see][chap.~22]{algo_2009}.
Furthermore, the parent $\rightarrow$ child sampling order can be reversed if the marginal probability of the child variable is known.
By Bayes' rule,

@@

A discretization policy $M_C = \anglebrackets{t_1 < t_2 < \ldots < t_{k-1}}$ for a continuous variable $C$ is a mapping from !!! mathbb{R} !!! to $\brock{1,2,3,\ldots,k}$ such that
\begin{equation}
  M_C (x)=\begin{cases}
    1, & \text{if $x<t_1$}.\\
    i, & \text{if $t_{i-1} \leq x < t_i$}\text{.}\\
    k, & \text{if $t_{k-1} \leq x$}
  \end{cases}
\end{equation}

@@

The section describes experiments designed to test the soundness of the proposed method. The experiments were run on four datasets from the Irvine repository \citep{Lichman:2013}. For each dataset, the experiment consists of two parts. In the first part, the Bayesian network structure is known in advance, which is obtained by equal-width prediscretization and the K2 algorithm. In the second part, the Bayesian netowrk structure is not provided in advance, and it is learned along with the discretization process.

For the case that network structure is given, a comparison between the proposed method and the MDL principle discretization is made. 10-fold cross validation of log-likelihood on data set $D_{\text{all}}$ is calculated as follows: firstly, learn discretization policies of each continuous variables from train data $D_{\text{train}}$. Secondly, obtain conditional probability tables $\phi_{x^* \mid \Pi^*_x}$ from the discretized train data $D^*_{\text{train}}$. Thirdly, For a test data instance $(x_1,x_2, \ldots, x_n)$ from $D_{\text{test}}$, the likelihood is
\begin{equation}
P(x_1, \ldots, x_n) = \prod_{i=1}^{n} \phi_{x^*_i \mid \Pi^*_{x_i}} \cdot \left( {1\over{M'_{X_i}[j_i+1] - M'_{X_i}[j_i]}} \right)^{\boldsymbol{1}_{ \left\lbrace X_i \text{ is continuous}  \right\rbrace }}
\end{equation}
, where $M'_{X_i}$ is the augmented discretization policy on continuous variable $X_i$ such that $M'_{X_i}[1] = min(D_{\text{all},X})$, $M'_{X_i}[j] = M_{X_i}[j-1]$ for $j=2,...,k_i$, and $M'_{X_i}[k_i+1] = max(D_{\text{all},X})$, $k$ is the number of intervals of continuous variable $X_i$ after discretization. Furthermore, $M'_{X_i}[j_i] \leq x_i < M'_{X_i}[j_i +1]$. This can be interpreted as follows: once a discrete-valued Bayesian network is learned from train data, test data are sampled from the learned network. If data is continuous, then it is uniformly sampled from the corresponding discretization interval.

\subsection{Dataset 1: Auto MPG} 
\label{subsec:autompg}

In this subsection, two experiments are conducted on the Auto MPG dataset from the Irvine repository \citep{Lichman:2013}. This dataset has 392 instances (delete the 6 instance with missing data) and eight variables. Three variables are discrete: $B$, $G$, and $H$ (in the following experiment, variables are named and ordered according to the dataset information webpage). They have 5, 13, and 3 cardinality numbers, respectively. In the first experiment, the network structure is given. In the second experiment, the network structure is not provided.

\subsubsection{Experiment 1 on Auto MPG dataset}
\label{subsubsec:autompg_exp1}
The proposed discretization method and the MDL discretization method are tested on the Bayesian network structure in Fig. \ref{Auto_graph_1}, which is obtained by running K2 algorithm 1000 times on prediscretized data, each time with a random restart. The prediscretization is done by equal-width discretization on continuous variables by 5 intervals (median of cardinalities of discrete variables). Shaded nodes in Fig. \ref{Auto_graph_1} means that they are discrete-valued variables.

\begin{figure}[ht]
\centering
    \begin{tabular}{cc}
      \input{graph_autocar_1}
    \end{tabular}
  \caption{The Bayesian network obatined by K2 algorithm and prediscretization on Auto MPG dataset}
  \label{Auto_graph_1}
\end{figure}

Table \ref{Auto_MPG_disc_table_1} shows the numbers of intervals after discretization, the positions of discretization edges, and log-likelihood of 10-fold cross validation. For the Bayesian network in Fig. \ref{Auto_graph_1}, the approximation only reduces runtime of proposed method and has no influence on discretization result. MDL principle discretization works not well, since it discretizes all variables with only one interval. For a Bayesian network on thie Auto MPG data set that MDL principle discretization has non-trivial result, please reference to Appendix.

\begin{table}
\centering
\scalebox{1.0}{
\input{table_autoMPG_1.tex}
}
\caption{Discretization result of Auto MPG dataset based on the graph in Fig. \ref{Auto_graph_1}}
\label{Auto_MPG_disc_table_1}
\end{table}

Figure \ref{auto_exp1_distr_1_3} compares the discretization result on continuous variables $A$ and $C$ with the raw data of Auto MPG data set. The color of discretized area shows the probability of a sample being in the discretized area. The black dots in Figure \ref{auto_exp1_distr_1_3} demonstrate the distribution of the raw data. As shown in the figure, the discretization edges and the resulting marginalized probability match the raw data very well.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_auto_exp1_distr_1_3}
    \end{tabular}
  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$}
  \label{auto_exp1_distr_1_3}
\end{figure}

\subsubsection{Experiment 2 on Auto MPG dataset}
\label{subsubsec:autompg_exp2}

If the network structure is not known in advance, it should be learned along with the discretization process. Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2} show a learned discrete-valued Bayesian network and the corresponding discretization edges of each continuous variable. This result is obtained by running Algorithm \ref{Learn_DBN} fifty times and choosing the one with the highest K2 score.
\newline

 {\centering
\begin{minipage}{0.50\textwidth}
  \centering
  \scalebox{0.7}{
  \input{graph_autocar_2}}
  \captionof{figure}{The learned discrete-\newline valued Bayesian network}
  \label{Auto_graph_2}
\end{minipage}
\begin{minipage}{0.50\textwidth}
  \raggedleft
  \input{table_autoMPG_2.tex}
  \captionof{table}{The discretization edges of variables in Fig \ref{Auto_graph_2}}
  \label{Auto_MPG_disc_table_2}
\end{minipage}
}

Figure \ref{auto_exp2_distr_1_3} compares the result of Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2} with the raw data on variables $A$ and $C$. Again, the black dots are raw data points. Although the numbers of discretization edges of $A$ and $C$ shown in Table \ref{Auto_MPG_disc_table_2} are less than Table \ref{Auto_MPG_disc_table_1}, they still have a good capture of raw data distribution.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_auto_exp2_distr_1_3}
    \end{tabular}
  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ according to Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2}}
  \label{auto_exp2_distr_1_3}
\end{figure}

\subsection{Dataset 2: Wine} 
\label{subsec:wine}

In this subsection, two experiments are conducted on the Wine dataset from the Irvine repository \citep{Lichman:2013}. This dataset has 178 instances and 14 variables. Only variable $A$ is discrete-valued with cardinality number 3. Again, in the first experiment, the network structure is given. In the second experiment, the network structure is not provided.

\subsubsection{Experiment 1 on Wine dataset}
\label{subsubsec:wine_exp2}

Figure \ref{Wine_graph_1} is obtained by equal-width discretizing each continuous variable into 3 intervals and running K2 1000 times. Table \ref{Wine_disc_table_1} shows a comparison between the proposed method and the MDL principle discretization method. The proposed method is still better than MDL principle discretization in terms of likelihood, although the latter returns non-trivial result in this experiment. Furthermore, the proposed method with the approximation has more intervals after discretization, thus it has a slightly better result. However, as shown in next dataset, the approximation might cut continuous variables into too many intervals. Therefore, the proposed method without the approximation should be still considered a better approach.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_1}
    \end{tabular}
  \caption{K2 structure learning with prediscretization on Wine dataset}
  \label{Wine_graph_1}
\end{figure}

\begin{table}
\centering
\scalebox{1.0}{
\input{table_wine_1.tex}
}
\caption{Discretization result of Wine dataset based on the graph Fig. \ref{Wine_graph_1}}
\label{Wine_disc_table_1}
\end{table}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_2}
    \end{tabular}
  \caption{K2 structure learning with the proposed discretization method on Wine dataset}
  \label{Wine_graph_2}
\end{figure}

\subsection{Data 3: Housing}
\label{subsec:housing}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_1}
    \end{tabular}
  \caption{K2 structure learning with prediscretization on Housing dataset}
  \label{Housing_graph_1}
\end{figure}

\begin{table}
\centering
\scalebox{1.0}{
\input{table_housing_1.tex}
}
\caption{Discretization result of Housing dataset based on the graph Fig. \ref{Housing_graph_1}}
\label{Housing_disc_table_1}
\end{table}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_housing_2}
    \end{tabular}
  \caption{K2 structure learning with the proposed discretization method on Housing dataset}
  \label{Housing_graph_2}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

### 2015-11-16 graph_auto_exp2_distr_1_3.tex
Add experiment part

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (15.2500,68.0000,0.0000) (15.2500,70.5000,0.0000) (9.0000,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.0000) (15.2500,70.5000,0.0000) (15.2500,93.5000,0.0000) (9.0000,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.0000) (15.2500,93.5000,0.0000) (15.2500,109.0000,0.0000) (9.0000,109.0000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.0020) (15.2500,109.0000,0.0020) (15.2500,159.5000,0.0020) (9.0000,159.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0235) (15.2500,159.5000,0.0235) (15.2500,259.0000,0.0235) (9.0000,259.0000,0.0235)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0030) (15.2500,259.0000,0.0030) (15.2500,284.5000,0.0030) (9.0000,284.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.1345) (15.2500,284.5000,0.1345) (15.2500,455.0000,0.1345) (9.0000,455.0000,0.1345)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000,0.0000) (17.6500,68.0000,0.0000) (17.6500,70.5000,0.0000) (15.2500,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.0000) (17.6500,70.5000,0.0000) (17.6500,93.5000,0.0000) (15.2500,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.0000) (17.6500,93.5000,0.0000) (17.6500,109.0000,0.0000) (15.2500,109.0000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.0020) (17.6500,109.0000,0.0020) (17.6500,159.5000,0.0020) (15.2500,159.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.0230) (17.6500,159.5000,0.0230) (17.6500,259.0000,0.0230) (15.2500,259.0000,0.0230)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.0030) (17.6500,259.0000,0.0030) (17.6500,284.5000,0.0030) (15.2500,284.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.0625) (17.6500,284.5000,0.0625) (17.6500,455.0000,0.0625) (15.2500,455.0000,0.0625)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000,0.0000) (20.9000,68.0000,0.0000) (20.9000,70.5000,0.0000) (17.6500,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.0000) (20.9000,70.5000,0.0000) (20.9000,93.5000,0.0000) (17.6500,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.0070) (20.9000,93.5000,0.0070) (20.9000,109.0000,0.0070) (17.6500,109.0000,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.0430) (20.9000,109.0000,0.0430) (20.9000,159.5000,0.0430) (17.6500,159.5000,0.0430)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.0880) (20.9000,159.5000,0.0880) (20.9000,259.0000,0.0880) (17.6500,259.0000,0.0880)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.0095) (20.9000,259.0000,0.0095) (20.9000,284.5000,0.0095) (17.6500,284.5000,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.0225) (20.9000,284.5000,0.0225) (20.9000,455.0000,0.0225) (17.6500,455.0000,0.0225)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000,0.0015) (25.6500,68.0000,0.0015) (25.6500,70.5000,0.0015) (20.9000,70.5000,0.0015)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.0060) (25.6500,70.5000,0.0060) (25.6500,93.5000,0.0060) (20.9000,93.5000,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.0320) (25.6500,93.5000,0.0320) (25.6500,109.0000,0.0320) (20.9000,109.0000,0.0320)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.0945) (25.6500,109.0000,0.0945) (25.6500,159.5000,0.0945) (20.9000,159.5000,0.0945)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.0455) (25.6500,159.5000,0.0455) (25.6500,259.0000,0.0455) (20.9000,259.0000,0.0455)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.0000) (25.6500,259.0000,0.0000) (25.6500,284.5000,0.0000) (20.9000,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.0070) (25.6500,284.5000,0.0070) (25.6500,455.0000,0.0070) (20.9000,455.0000,0.0070)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000,0.0055) (28.9000,68.0000,0.0055) (28.9000,70.5000,0.0055) (25.6500,70.5000,0.0055)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.0110) (28.9000,70.5000,0.0110) (28.9000,93.5000,0.0110) (25.6500,93.5000,0.0110)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.0375) (28.9000,93.5000,0.0375) (28.9000,109.0000,0.0375) (25.6500,109.0000,0.0375)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.0545) (28.9000,109.0000,0.0545) (28.9000,159.5000,0.0545) (25.6500,159.5000,0.0545)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.0165) (28.9000,159.5000,0.0165) (28.9000,259.0000,0.0165) (25.6500,259.0000,0.0165)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.0000) (28.9000,259.0000,0.0000) (28.9000,284.5000,0.0000) (25.6500,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.0035) (28.9000,284.5000,0.0035) (28.9000,455.0000,0.0035) (25.6500,455.0000,0.0035)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000,0.0030) (46.6000,68.0000,0.0030) (46.6000,70.5000,0.0030) (28.9000,70.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.0995) (46.6000,70.5000,0.0995) (46.6000,93.5000,0.0995) (28.9000,93.5000,0.0995)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.0860) (46.6000,93.5000,0.0860) (46.6000,109.0000,0.0860) (28.9000,109.0000,0.0860)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.0605) (46.6000,109.0000,0.0605) (46.6000,159.5000,0.0605) (28.9000,159.5000,0.0605)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.0120) (46.6000,159.5000,0.0120) (46.6000,259.0000,0.0120) (28.9000,259.0000,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,284.5000,0.0000) (28.9000,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.0005) (46.6000,284.5000,0.0005) (46.6000,455.0000,0.0005) (28.9000,455.0000,0.0005)};

>>>>

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (17.5500,68.0000,0.0000) (17.5500,134.5000,0.0000) (9.0000,134.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.0010) (17.5500,134.5000,0.0010) (17.5500,159.5000,0.0010) (9.0000,159.5000,0.0010)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0010) (17.5500,159.5000,0.0010) (17.5500,169.5000,0.0010) (9.0000,169.5000,0.0010)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.0395) (17.5500,169.5000,0.0395) (17.5500,259.0000,0.0395) (9.0000,259.0000,0.0395)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0045) (17.5500,259.0000,0.0045) (17.5500,264.5000,0.0045) (9.0000,264.5000,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.2220) (17.5500,264.5000,0.2220) (17.5500,455.0000,0.2220) (9.0000,455.0000,0.2220)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.0765) (23.9500,68.0000,0.0765) (23.9500,134.5000,0.0765) (17.5500,134.5000,0.0765)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.0260) (23.9500,134.5000,0.0260) (23.9500,159.5000,0.0260) (17.5500,159.5000,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.0085) (23.9500,159.5000,0.0085) (23.9500,169.5000,0.0085) (17.5500,169.5000,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.1225) (23.9500,169.5000,0.1225) (23.9500,259.0000,0.1225) (17.5500,259.0000,0.1225)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.0070) (23.9500,259.0000,0.0070) (23.9500,264.5000,0.0070) (17.5500,264.5000,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.0355) (23.9500,264.5000,0.0355) (23.9500,455.0000,0.0355) (17.5500,455.0000,0.0355)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.3525) (46.6000,68.0000,0.3525) (46.6000,134.5000,0.3525) (23.9500,134.5000,0.3525)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.0770) (46.6000,134.5000,0.0770) (46.6000,159.5000,0.0770) (23.9500,159.5000,0.0770)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.0020) (46.6000,159.5000,0.0020) (46.6000,169.5000,0.0020) (23.9500,169.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.0210) (46.6000,169.5000,0.0210) (46.6000,259.0000,0.0210) (23.9500,259.0000,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,264.5000,0.0000) (23.9500,264.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.0035) (46.6000,264.5000,0.0035) (46.6000,455.0000,0.0035) (23.9500,455.0000,0.0035)};

### 2015-11-16 test2.tex
Add experiment part

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=A,
			ylabel=C,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=A,
			ylabel=C,
			colorbar,
			point meta min=0, point meta max=0.25,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.25},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

### 2015-11-16 test_2.tex
Add experiment part

 \begin{tikzpicture}
        \begin{axis}%[
            view={0}{90},
            xlabel=quantity of wine,
            ylabel=grape quality,
            colorbar,
            colormap/blackwhite
            ]
			%\addplot[color=red]{exp(x)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,0,   1) (1,0,   0) (1,1.25,0) (0,1.25,0.1)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,1.25,1) (1,1.25,0) (1,2,   0) (0,2,   0.2)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,2,   1) (1,2,   0) (1,3,   0) (0,3,   0.3)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,0,   1) (2.5,0,   0) (2.5,1.25,0) (1,1.25,0.15)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,1.25,1) (2.5,1.25,0) (2.5,2,   0) (1,2,   0.25)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,2,   1) (2.5,2,   0) (2.5,3,   0) (1,3,   0.05)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,0,   1) (3,0,   0) (3,1.25,0) (2.5,1.25,0.25)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,1.25,1) (3,1.25,0) (3,2,   0) (2.5,2,   0.1)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,2,   1) (3,2,   0) (3,3,   0) (2.5,3,   0.3)};
        \end{axis}
\end{tikzpicture}

>>>>

\documentclass[crop,tikz]{standalone}

\usepackage{pgfplots}
\usepackage[separate-uncertainty=true,detect-mode=true]{siunitx}

\begin{document}

    \begin{tikzpicture}
        \begin{axis}[
            view={0}{90},
            xlabel=quantity of wine,
            ylabel=grape quality,
            colorbar,
            colormap/blackwhite
            ]

            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,0,   1) (1,0,   1) (1,1.25,1) (0,1.25, 1)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,1.25,1) (1,1.25,0) (1,2,   0) (0,2,   0.2)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0,2,   1) (1,2,   0) (1,3,   0) (0,3,   0.3)};

            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,0,   0) (2.5,0,   0) (2.5,1.25,0) (1,1.25,0)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,1.25,1) (2.5,1.25,0) (2.5,2,   0) (1,2,   0.25)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1,2,   1) (2.5,2,   0) (2.5,3,   0) (1,3,   0.05)};

            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,0,   1) (3,0,   0) (3,1.25,0) (2.5,1.25,0.25)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,1.25,1) (3,1.25,0) (3,2,   0) (2.5,2,   0.1)};
            \addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5,2,   1) (3,2,   0) (3,3,   0) (2.5,3,   0.3)};
        \end{axis}
    \end{tikzpicture}

    % \label{fig:plot_label}
    % \caption{Probability density under MODL discretization for two variables from the Wine dataset}
\end{document}
